Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-10 paper/paper.Rmd
tweak figure labels

relative_summary <- relative_wis_by_horizon |>
  merge(
    relative_ae_by_horizon, by = c("horizon", "model")
  ) |>
  melt(
    measure.vars = c("Weighted interval score", "Absolute error of the median")
  )

>>>>

relative_summary <- relative_wis_by_horizon |>
  merge(
    relative_ae_by_horizon, by = c("horizon", "model")
  ) |>
  melt(
    measure.vars = c("Weighted interval score", "Absolute error")
  )
